Model Search in Relational Domains

### 2016-10-22 decision.tex
sync
decision text

\subsection{Decision}
A decision $\decisionvar$ is a meet irreducible that refines the
current abstract value $\abs(\trail)$.  Note that meet irreducibles in
relational domains may involve several variables.
%
% For example, a decision in interval 
%domain can be of the form $\langle x R c \rangle$ where 
%$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
%relational domain such as octagon is of the form $ax - by \leq c$, 
%where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
%and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
%
Hence, a decision can specify a relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\trail$, i.e.\ $\abs(\trail\cdot \decisionvar)\neq \bot$.  
A new decision always increases the decision level by one.

We call a \emph{singleton} a meet irreducible which does represent a
valid decision.
%
For template polyhedra, singletons are the meet irreducibles
corresponding to a pair of rows $\vec{c}_1,\vec{c}_2$ in matrix
$\mat{C}$ with $\vec{c}_1\vec{\numvar}=-\vec{c}_2\vec{\numvar}$
(i.e.\ \emph{matching} rows) and the corresponding bounds
$\numabsval_1=-\numabsval_1$.
%
A singleton in the interval domain corresponds to a singleton interval
such as $x\leq 1 \wedge -x\leq -1$ For the octagon domain, $1 \leq x-y
\leq 1$ is a singleton.
%
We cannot make decisions for template rows of singletons because there
is no choice left. Similarly, in a SAT solver, we cannot make a
decision on a variable that is already assigned $\true$ or $\false$.
%
Note that for relational domains singletons do not necessarily
concretise to singleton sets of concrete values for the variables
involved.

@@

We implemented several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random} and the 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordered heuristic is similar to trace partitioning~\cite{toplas07}.

The {\em longest-range} heuristics simply keeps track of the bounds
$numabsval_l,numabsval_u$ of matching template rows $\numabsval_l\leq
\vec{c}\vec{x}\leq \numabsval_u$, picks the one with the longest range
$\numabsval_u-\numabsval_l$, and randomly returns the meet irreducible
$\vec{c}\vec{x}\leq
\lfloor\frac{\numabsval_l+\numabsval_u}{2}\rfloor$ or its
complement. This ensures a fairness policy in selecting a variable
since it guarantees that the intervals of meet irreducibles are
uniformly restricted.
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. %\pscmt{uniformly?}
%
%The {\em relational} decision heuristics is only relevant for relational 
%abstract domains.  
%
The {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The Berkmin heuristics %is currently implemented for interval constraints only.  
%The heuristic 
keeps track of the activity of %an interval 
meet irreducibles that participate in conflict clauses. 
Based on the most active meet irreducible, ranges a split similar to the {\em longest-range} heuristics.
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organised chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
%A bound of a meet irreducible is heuristically chosen to be an
%approximation of the arithmetic average of the current bounds.
%However, the polarity ($\leq$ or $\geq$) of a meet irreducible is
%chosen randomly.

>>>>

\subsection{Decision}
A decision $\decisionvar$ is a meet irreducible that refines the
current abstract value $\abs(\trail)$.  Note that meet irreducibles in
relational domains may involve several variables.
%
% For example, a decision in interval 
%domain can be of the form $\langle x R c \rangle$ where 
%$R \in \{\leq, \geq\}$, $c$ is the bound.  A decision in 
%relational domain such as octagon is of the form $ax - by \leq c$, 
%where $x$ and $y$ are variables, $a,b \in \{-1,0,1\}$ are co-efficients, 
%and $c \in \mathbb{R}\cup\{\infty\}$ is the bound of the inequality.  
%
Hence, a decision can specify relation between variables, for example 
$\{x \leq y)$.  A decision must always be consistent with respect to 
the trail $\trail$, i.e.\ $\abs(\trail\cdot \decisionvar)\neq \bot$.  
A new decision always increases the decision level by one.

\rmcmt{We call a \emph{singleton} a meet irreducible which does represent a
valid decision ??}.
%
For template polyhedra, singletons are the meet irreducibles
corresponding to a pair of rows $\vec{c}_1,\vec{c}_2$ in matrix
$\mat{C}$ with $\vec{c}_1\vec{\numvar}=-\vec{c}_2\vec{\numvar}$
(i.e.\ \emph{matching} rows) and the corresponding bounds
$\numabsval_1=-\numabsval_1$.
%
A singleton in the interval domain corresponds to a singleton interval
such as $x\leq 1 \wedge -x\leq -1$ For the octagon domain, $1 \leq x-y
\leq 1$ is a singleton.
%
We cannot make decisions for template rows of singletons because there
is no choice left. Similarly, in a SAT solver, we cannot make a
decision on a variable that is already assigned $\true$ or $\false$.
%
Note that for relational domains singletons do not necessarily
concretise to singleton sets of concrete values for the variables
involved.

@@

We have implemented several decision heuristics namely, {\em ordered}, 
{\em longest-range}, {\em random} and the 
{\em Berkmin}~\cite{eugoldberg07} decision heuristics.  
The {\em ordered} decision heuristics creates an ordering among non-singleton 
meet irreducibles, thereby making decisions on meet irreducibles that involve 
conditional variables (variables that appear in conditional branches) first 
before choosing meet irreducibles with numerical variables.  
The ordered heuristic is similar to trace partitioning~\cite{toplas07}.

The {\em longest-range} heuristics simply keeps track of the bounds
$\numabsval_l,\numabsval_u$ of matching template rows $\numabsval_l\leq
\vec{c}\vec{x}\leq \numabsval_u$, picks the one with the longest range
$\numabsval_u-\numabsval_l$, and randomly returns the meet irreducible
$\vec{c}\vec{x}\leq
\lfloor\frac{\numabsval_l+\numabsval_u}{2}\rfloor$ or its
complement. This ensures a fairness policy in selecting a variable
since it guarantees that the intervals of meet irreducibles are
uniformly restricted.
%
The {\em random} decision heuristics arbitrarily picks a meet irreducible  
for making decision. \pscmt{uniformly?}
%
%The {\em relational} decision heuristics is only relevant for relational 
%abstract domains.  
%
The {\em berkmin} decision heuristics is inspired 
from decision heuristic used in Berkmin~\cite{eugoldberg07} SAT solver.  
The Berkmin heuristics %is currently implemented for interval constraints only.  
%The heuristic 
keeps track of the activity of %an interval 
meet irreducibles that participate in conflict clauses. 
Based on the most active meet irreducible, ranges a split similar to the {\em longest-range} heuristics.
\Omit {
as well as variables that actively contribute to conflicts but do not explicitly 
appear in conflict clauses.  The set of conflict clauses is 
organised chronologically with the top clause 
as the one deduced in the last.  A branching variable is chosen among the 
free variables whose literals are in the top unsatisfied conflict clause.  
A similar decision heuristics is also implemented in Chaff~\cite{chaff} SAT 
solver, that computes the activity of a variable as the number of occurrences 
of that variable in conflict clauses only. 
}
%
%A bound of a meet irreducible is heuristically chosen to be an
%approximation of the arithmetic average of the current bounds.
%However, the polarity ($\leq$ or $\geq$) of a meet irreducible is
%chosen randomly.
